Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
add the second talk by Dan Gunter

\item \textbf{Dan Gunter, Adam Arkin, Rick Stevens, Robert Cottingham and
Sergei Maslov: \textit{Challenges of a Sustainable Software Platform for Predictive
Biology: Lessons Learned on the KBase Project}}

>>>>

\item \textbf{Dan Gunter, Adam Arkin, Rick Stevens, Robert Cottingham and
Sergei Maslov: \textit{Challenges of a Sustainable Software Platform for Predictive
Biology: Lessons Learned on the KBase Project}}
In this talk, Dan Gunter presented experiences and lessons learned as part of
KBase, an open software and data platform for addressing the grand challenge of
systems biology: predicting and designing biological function. KBase is a
unified system that integrates data and analytical tools for comparative
functional genomics of microbes, plants, and their communities. However,
it is also a collaborative environment for sharing methods and results, and
placing those results in the context of knowledge in the field. Being a large,
multiinstutional project, one the big challenges is to agree on standard to
enable a single, maintainable system. Working in isolation does not work (anymore)
within this field, and no standards for software engineering existed either.
This is contrasted to computer science research, where these approaches can lead to
shorter design cycles, leading to more time for highly rewarded activities like
publishing, performance studies, graduating students, or protecting ideas
before publication. Sustainability is not of big concern there, compared to
these. Instead of this more traditional approach, the following is used within
KBase for large, distributed teams. After picking projects and team members, a
number of 4-5 teams uses about two weeks to work on their project before a
1-week evaluation by the executive committee, and after which new teams and
projects might be chosen to restart the ``agile'' development cycle. This
process is intentionally open and documented.
